---
title: "Lab 01 - Hello R"
author: "Adam Paul"
date: "1/21/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

A data frame with 1846 rows and 3 variables (which serve as the columns). The three variables are 'dataset', which indicates which set the data are from. 'x-values' and 'y-values'.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation is -0.06447185.

### Exercise 3

I began by creating the data frame 'star_data', made by removing all references to dino in the original code. Specifically, a change was made in line 47 to 'star_data' and line 48 to 'star'.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

I adopted the text from above, making the change of swapping 'dino' out for 'star'. Since the variable names share the same root '_data' I only swapped out star.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation is -0.0629611. 

As a brief aside, it wasn't until this step that I noticed you wanted specific commit details. Therefore, this is the first one that has the proper commit information. It's also worth noting that I find committing and pushing via Git desktop a lot more intuitive, and have been doing so that way. If this is wrong for some reason, please let me know.

### Exercise 4

Below follows the creation of the data frame circle_data, which isolates the dataset circle from within datasaurus_dozen. In the same chunk, I also create the plot for circle_data.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Below, I calculate the correlation for circle_data.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation is -0.06834336. 

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
